---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Keyword.Scatter

<!-- badges: start -->
<!-- badges: end -->

Keyword.Scatter is a package created for assigment 2 of my STAT-545B course. The package contains the function `kw_scatter()`, which creates a ggplot scatter graph from a tibble that has been filtered by the chosen keyword contained in a chosen column.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("timcrowe91/Keyword.Scatter")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Keyword.Scatter)
library(gapminder)
library(dplyr)

1 + 1
# TEST WITH "..." ----- alpha transparency etc... put it in the geom_point() ?
#kw_scatter(data = gapminder, keyword = "United", keyword_column = country, x = lifeExp, y = gdpPercap)

```

## Step By Step Process To Create Package

1. create_package() to start the "Keyword.Scatter" package
2. use_git() to convert it to a git repository
3. In terminal:
    * "git remote add origin https://github.com/timcrowe91/Keyword.Scatter" to connect my local repo to GitHub
    * "git push -u origin master" to push everything to my GitHub repo
4. use_r("Keyword") to create the script to put my function in
5. use_readme_rmd() to create README file
6. build_readme() to render README (ongoing)
7. Manually edited DESCRIPTION file in R-Studio to input title, author, description
8. use_mit_license("Tim Crowe")
9. Used Roxygen to create documentation and rendered using document()
10. use_testthat() to create files for tests
11. use_test("kw_scatter") to create test script for function, and filled with tests from assigment 1b

